---
title: "Final Project Draft"
subtitle: "Draft"
author: "Ethan Miller"
date: "08 April, 2026"
output: 
  html_notebook:
    fig_height: 7
    fig_width: 10
---

<body style="background-color:lightgrey;">

\# Temporary to make it easier to look at since it's white by default.

```{r include = FALSE}
# Load packages: `tidyverse`, `lubridate` (if others are needed, load them here)
library(lubridate)
library(tidyverse)
library(esquisse)
library(dplyr)
library(here)

# Packages loaded for A.5 leaflet graphic
library(devtools)
library(leaflet)

# Load data + objects


source(here("Data and Plots", "Final.R"))
```

<h1 style="text-align: center;">

Where Are my Representatives Getting Their Money?

</h1>

No matter your politics, voting is an essential part of a democratic society. It is our responsibility as individuals to participate in elections to make our voices heard and ensure the needs of our community are met. With this in mind, I decided to make my project about the campaign finances of the two front runners for the congressional elections in November in Maryland's 6th district.

The goal of this project is not to unpack the specific policies that these candidates will be running on, but to analyze where their funding is coming from that allows them to run for congress in the first place. The two candidates I will be focusing on are David Trone, and the incumbent, April McClain Delaney. At its core, this project asks a simple question: where does their money come from?

## Why Finances Matter

During election cycles, we’re inundated with ads, commercials, and rallies outlining what candidates say they’ll do if elected. We hear what they want to change and what they believe the current representative has gotten wrong. That messaging is an important part of any campaign, but it only tells part of the story.

None of these promises happen without money. Campaigns are powered by funding, and where that money comes from matters. Candidates may self-finance, receive contributions from organizations or corporations, accept support from Political Action Committees, or rely on individual donors. Each of these sources, and the amounts they contribute, helps tell a deeper story about a campaign’s priorities, backing, and potential influence.

## Where the Data Comes From

All the data that I have accumulated for this project comes from [FEC.GOV](https://www.fec.gov). This website hosts the Federal Election Commission, an "independent regulatory agency charged with administering and enforcing the federal campaign finance law." Part of this work consists of aggregating campaign contribution data and making it accessible to the public. This information is being updated in real time, but I pulled data on March 17th 2026.

## What I Want to Learn

My goal is understanding the financial side of these campaigns. I want to know how much each candidate contributes to their own campaign, who their donors are, where those donors are located, and how much they give. I’m also interested in the proportion of funding that comes from different types of donors, as well as mapping where contributors live to see whether out-of-state money plays a role.

## Summary

This project aims to answer a few key questions:

-   How much risk is a candidate taking upon themselves?

-   What proportion of funding comes from the different types of donors?

-   Who is donating to each campaign?

-   How much are they contributing?

-   Where are these donors located?

## Preliminary Analysis

As I said before, the data I'm using comes from the FEC. The structure of the data for both candidates is identical, and there are many variables that are not important to the analysis I will be doing. Because of this, I've created a data frame that combines both candidates data and removed all columns I found to be unnecessary.

I would like to note, David Trone's base data shows several committee names:

```{r}
trone_data_raw %>% 
  group_by(committee_name) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))
```

Because of this, I've mutated the committee name to combine all different committees under one common name "David Trone fo Congress". For the purposes of this project, differentiating between the various committees is unimportant.

```{r}
# Combine all data sets
all_data <- rbind(delaney_data, trone_data) %>% 
  select(committee_id, committee_name, report_year, transaction_id, 
         file_number, entity_type, entity_type_desc, unused_contbr_id, 
         contributor_name, recipient_committee_designation, contributor_first_name, 
         contributor_middle_name, contributor_last_name, contributor_suffix, 
         contributor_street_1, contributor_street_2, contributor_city, 
         contributor_state, contributor_zip, contributor_employer, contributor_occupation, 
         contributor_id, is_individual, receipt_type_desc, memo_text, 
         contribution_receipt_date, contribution_receipt_amount, contributor_aggregate_ytd, 
         candidate_name, candidate_first_name, candidate_last_name, candidate_middle_name, 
         candidate_office_state, candidate_office_state_full, candidate_office_district, 
         conduit_committee_id, donor_committee_name, fec_election_year, two_year_transaction_period)
sample_n(all_data, 10)
```

As we scroll a random set of 10 rows of combined data, we can see that the variables are already coded as they should be.

### Let us first see how long each candidate has been in politics:

```{r}
minYear <- all_data %>% 
  group_by(committee_name) %>% 
  summarise(minYear = min(report_year))
minYear
```

This shows us that Trone has been in politics for much longer than Delaney. This will be necessary to keep in mind when comparing financial data, as Trone has 7 years more data than Delaney.

## Risk:

What I want to know first is how much risk each candidate has taken by running for office. I want to know exactly how much each candidate has contributed to their own campaign.

```{r}
ind_cont <- all_data %>% 
  group_by(committee_name) %>% 
  mutate(years_active = n_distinct(report_year)) %>% 
  ungroup() %>% 
  filter(entity_type_desc == "CANDIDATE") %>% 
  group_by(committee_name, entity_type_desc) %>% 
  summarise(
    total = sum(contribution_receipt_amount),
    years_active = max(years_active),
    spend_per_year = total / years_active,
    .groups = "drop"
  )

ind_cont
```

This data tells two different stories. Considering just the total spend per candidate, Trone has outspent Delaney by a wide margin. Considering time in office smooths that number out considerably.

```{r}
## Plot to represent difference:
ggplot(ind_cont) +
  aes(x = committee_name, y = total/1000000, fill = committee_name) +
  geom_col() +
  labs(
    x = "Candidate",
    y = "Personal Contribtion (in Millions)",
    title = "Personal Campaign Contributions",
  ) +
  theme_minimal() +
  theme(axis.text.y = element_text(angle = 45L),
        legend.position = "none")

```

At first glance, the difference between 4.5 million from Delaney and a whopping 114 million dollars from Trone looks like Trone is taking on considerable risk. Taking a closer look at the context helps explain this disparity.

David Trone is the co-founder of [Total Wine](https://www.forbes.com/sites/lizthach/2024/02/14/how-total-wine--more-became--largest-us-wine-retailer/), an alcohol retailer valued at roughly 2.4 billion dollars. Knowing this makes his self funding look less like risk and more like a strategic investment in policy outcomes that affect his industry.

Maryland is one of four states in the country that does not allow beer and wine to be sold in grocery stores. The founder of the nation’s largest alcohol retailer has a clear stake in legislation that could reshape alcohol distribution. A voter has the right to know that their representative has a stake in an industry that may be impacted by changes in legislation.

With that said, Delaney isn't hurting for cash either. Her personal financial disclosure shows she has a substantial portfolio. The website [Quiver Quantitative](https://www.quiverquant.com/congresstrading/politician/April%20McClain%20Delaney-M001232/net-worth) estimates her net worth is just shy of 153 million dollars.

## Conclusion

Both Trone and Delaney are some of the wealthiest people in congressional politics. Given this fact, neither candidate has assumed considerable risk in their run for office. Both candidates have more than enough money to comfortably run for office.

More importantly, this breakdown suggests the opposite of risk. Both candidates have a vested interest in driving legislation in a given direction.

## What proportion of funding comes from the different types of donors?

Now I'd like to see how much money each candidate receives from outside donations. Because we have already observed each candidates personal finances and contributions, we will be excluding any personal contributions from the candidate or their committee. To do this, I've written a custom function:

```{r}
df_filtered <- function(df) {
  df %>%
    filter(
      !entity_type_desc %in% c("CANDIDATE", "CAMPAIGN COMMITTEE", 
                               "POLITICAL PARTY COMMITTEE", "OTHER COMMITTEE"),
      contribution_receipt_amount > 0,
      report_year >= 2020,
      contributor_name != "ACTBLUE",
      !grepl("\\bRE", memo_text, ignore.case = TRUE))
}
```

What this does is filter out any candidate contributions, either direct or through their campaign. This also excludes negative contributions (reimbursements or refunds) and sets the minimum year as 2020 to better represent current data. I've also excluded the contributor "ActBlue". To my understanding, this is an organization that contributes to democratic campaigns. Each ActBlue contribution has a corresponding individual contribution in both candidates base data. Removing ActBlue essentially removes duplicate contributions.

```{r}
summarize_finances <- function(df) {
  df_filtered(df) %>% # apply the filter first
    group_by(entity_type_desc) %>%
    summarise(total = sum(contribution_receipt_amount, na.rm = TRUE), .groups = "drop") %>%
    mutate(prop = round((total / sum(total))*100, 2)) %>%
    arrange(desc(total))
}

trone_fin_dist <- summarize_finances(trone_data) %>% mutate(candidate = "Trone")

trone_fin_dist
```

```{r}
delaney_fin_dist <- summarize_finances(delaney_data) %>% mutate(candidate = "Delaney")

delaney_fin_dist
```

```{r}
all_dist <- bind_rows(trone_fin_dist, delaney_fin_dist)

# Campaign Contribution by Entity Type ------------------------------------
ggplot(all_dist) + 
  aes(x = entity_type_desc, y = total, fill = candidate) +
  geom_col(position = "dodge", stat = "identity") +
  
  geom_text(
    aes(label = scales::comma(total)),
    position = position_dodge(width = 0.9),
    vjust = -0.3,
    size = 3
  ) +
  
  theme(
    panel.grid.minor = element_blank(),
    plot.margin = margin(6, 8, 6, 8),
    axis.text.y = element_text(angle = 40, hjust = 1, vjust = 1),
    legend.position = "bottom"
  ) +
  
  scale_y_continuous(labels = dollar) +
  
  labs(
    title = "Contribution Totals by Entity Type",
    x = NULL,
    y = "Total Contributions"
  ) +
  theme_minimal()
```

As shown above, both candidates receive contributions form three primary sources:

-   Individuals

-   Organizations

-   Political Action Committees (PACs)

Now that the types of donors have been established, we can drill-down into each category to learn more.

### Individuals

A small individual donation is considered a contribution of less than \$200. What these small donations represent are ordinary people donating to a campaign. I'd like to observe the proportion of individual donations that can be considered small.

```{r}
small_donations <- df_filtered(all_data) %>% 
  filter(entity_type_desc == "INDIVIDUAL") %>% 
  group_by(committee_name) %>% 
  summarise(
    total = sum(!is.na(contribution_receipt_amount)),
    sd_count = sum(contribution_receipt_amount <= 200, na.rm = TRUE),
    ld_count = sum(contribution_receipt_amount >= 201, na.rm = TRUE),
    sd_prop = sd_count / total,
    ld_prop = ld_count / total
  )
small_donations
```

```{r}
stack_donations <- small_donations %>% 
  select(committee_name, sd_prop, ld_prop) %>% 
  pivot_longer(
    cols = c(sd_prop, ld_prop),
    names_to = "type",
    values_to = "prop"
  ) %>% 
  mutate(type = recode(type,
         sd_prop = "Small (≤200)",
         ld_prop = "Large (>200)"),
         committee_name = str_wrap(committee_name, width = 20))

ggplot(stack_donations, aes(x = committee_name, y = prop, fill = type)) +
  geom_col() +
  geom_text(
    aes(label = percent(prop, accuracy = 0.1)),
    position = position_stack(vjust = 0.5),
    size = 3
  ) +
  labs(
    title = "Donation Proportion by Candidate",
    x = NULL,
    y = "Number of Donations",
    fill = "Donation Size"
  ) +
  theme_minimal()
```

The statistics continue to be unflattering for both candidates. Here we see that Trone and Delaney both receive the vast majority of their individual donations from large donors, greater than \$200.

For the sake of argument, let's look at donations greater than \$1000 and see if the stats change:

```{r}
med_donations <- df_filtered(all_data) %>% 
  filter(entity_type_desc == "INDIVIDUAL") %>% 
  group_by(committee_name) %>% 
  summarise(
    total = sum(!is.na(contribution_receipt_amount)),
    sd_count = sum(contribution_receipt_amount <= 1000, na.rm = TRUE),
    ld_count = sum(contribution_receipt_amount >= 1001, na.rm = TRUE),
    sd_prop = sd_count / total,
    ld_prop = ld_count / total
  )
med_donations
```

```{r echo=FALSE}
stack_med_donations <- med_donations %>% 
  select(committee_name, sd_prop, ld_prop) %>% 
  pivot_longer(
    cols = c(sd_prop, ld_prop),
    names_to = "type",
    values_to = "prop"
  ) %>% 
  mutate(type = recode(type,
         sd_prop = "Small to Medium (≤1000)",
         ld_prop = "Larger (>1000)"),
         committee_name = str_wrap(committee_name, width = 20))

ggplot(stack_med_donations, aes(x = committee_name, y = prop, fill = type)) +
  geom_col() +
  geom_text(
    aes(label = percent(prop, accuracy = 0.1)),
    position = position_stack(vjust = 0.5),
    size = 3
  ) +
  labs(
    title = "Donation Proportion by Candidate",
    x = NULL,
    y = "Number of Donations",
    fill = "Donation Size"
  ) +
  theme_minimal()
```

Even after changing the small and large to over / under \$1000, both candidates have a quarter or more of their donations from very large individual donations.

Most voters are not in a position to donate to campaigns, and giving more than \$1,000 is out of reach for many. These numbers show how much campaign funding depends on a relatively small group of high-dollar donors and how strongly those donors shape the political landscape.

Speaking of high-dollar influence, who might be our max donors?

```{r}
max_donors <- all_data %>% 
  filter(entity_type_desc == "INDIVIDUAL") %>% 
  mutate(amount = as.numeric(contribution_receipt_amount)) %>% 
  group_by(committee_name, contributor_name) %>%
  summarise(
    total = sum(amount, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  group_by(committee_name) %>% 
  slice_max(total, n = 3, with_ties = FALSE) %>% 
  ungroup()

max_donors
```

Let us go down the list and see who these folks are,

For Delaney:

-   [Daniel Lennon](https://www.lw.com/en/people/daniel-lennon) - former Global Chair of the firm’s Corporate Department and former Washington, D.C. Office Managing Partner, focused on corporate transactions.

-   [Michael Karam](https://www.linkedin.com/in/michael-karam-786bab10/) - Georgetown University Alumni Association Board of Governors

-   [Anne Arcano](https://nysba.org/justice-for-all-luncheon-2021/?srsltid=AfmBOorCagdPPql7SD_V7_k9YCrglykYTVEEqBjXqDiHzAaiqA3vXe0Q) - Lawyer with a background in tax and family law.

For Trone:

-   [Robert Epstein](https://www.umasshillel.org/speakers.html) No, not that Epstein... President & Chief Executive Officer at Horizon Beverage, a leading beverage company.

-   [Ronald Abramson](https://www.bipc.com/ronald-abramson) Serves on the Board of Total Wine

-   [Neal Wilson](https://www.ejfcap.com/people/neal-wilson/) Co-Chief Executive Officer & Co-Chief Investment Officer, EJF Capital

It is important to recognize that these names are not random outliers. They are people with significant professional, financial, and social capital. The top donors to both campaigns are overwhelmingly drawn from executive leadership, corporate law, finance, and board-level positions. In other words, the individuals most capable of giving large sums are also those most embedded in institutions with a direct stake in public policy.

### Organizations

As we saw above, neither candidate received much at all from organizations. After filtering out refunds, each candidate is left with no more than \$15,000.

Even still, understanding what organizations are giving money to their campaigns shows us a clearer picture of who the candidates claim to represent.

```{r}
summarize_donors <- function(df) {
  df_filtered(df) %>% 
    filter(entity_type_desc == "ORGANIZATION") %>% 
    group_by(contributor_name) %>% 
    summarise(
      total = sum(contribution_receipt_amount, na.rm = TRUE), .groups = "drop") %>% 
    slice_max(total, n = 5, with_ties = FALSE) %>% 
    arrange(desc(total))
}

summarize_donors(trone_data)
```

```{r}
summarize_donors(delaney_data)
```

While the contributions are relatively small, they tell an interesting story.

For Trone:

-   [LAKEFRONT 17, LLC](https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://www.mapquest.com/us/maryland/lakefront-17-llc-553071264&ved=2ahUKEwj0iNjNqOiTAxUSkokEHYX1CcIQFnoECB4QAQ&usg=AOvVaw2l7O38c-yl3ZQ1thW6ngqM) is a property management company based in Columbia, MD.

-   [THE ORENDA CENTER FOR WELLNESS LLC](https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://theorendacenter.com/&ved=2ahUKEwiT2sLlpeiTAxXphIkEHZ2JO8EQFnoECCgQAQ&usg=AOvVaw0flL0h41cVFfwjh320DBlp) is a center for addiction treatment.

-   [BLUE CROSS BLUE SHIELD](https://www.bcbs.com) is an insurance company.

For Delaney:

-   PERRY PARKWAY ASSOCIATES LP does not appear to have an online presence at all. The business has been registered, but it is unclear what it does. It may be a property management company for hotels.

-   [GAMBRILL VIEW DEVELOPMENT LLC](https://gambrillviewfrederick.com) is a property management company.

-   [TAID LLC](https://www.taid.ai) is some sort of training or education service that uses AI.

Trone receiving money from the Orenda Center for Wellness tracks with his messaging on addiction. Delaney receiving money from property management companies and AI services gives insight to potential policy decisions she may make.

Also, Delaney receiving a donation from the MD Democratic Party is very interesting. To me, this shows that establishment democrats are more confident in Delaney than they are Trone. 

Given that neither candidate received a considerable amount from any organization, we can't reasonably draw any conclusions as to what interests they represent for businesses.

### PACs
[PACs (political action committees)](https://www.fec.gov/press/resources-journalists/political-action-committees-pacs/) essentially bridge the gap between corporations and individuals. They pool contributions from members or affiliated supporters and direct those funds toward candidates and causes that reflect their shared priorities.

In doing so, PACs play a dual role: they advocate for specific policy positions while also channeling financial support to campaigns they view as aligned with those goals.

Like the organization data, I want to know what PACs are donating and how much.
```{r}
summarize_PAC <- function(df) {
  df_filtered(df) %>% 
    filter(entity_type_desc == "POLITICAL ACTION COMMITTEE") %>% 
    group_by(contributor_name) %>% 
    summarise(
      total = sum(contribution_receipt_amount, na.rm = TRUE), .groups = "drop") %>% 
    slice_max(total, n = 5, with_ties = FALSE) %>% 
    arrange(desc(total))
}

trone_PAC <- summarize_PAC(trone_data) %>% mutate(cand = "Trone")
```

```{r}
delaney_PAC <- summarize_PAC(delaney_data) %>% mutate(cand = "Delaney")
```
```{r}
allPAC <- bind_rows(trone_PAC, delaney_PAC) %>%
  mutate(contributor_name = case_when(
    grepl("ISRAEL", contributor_name, ignore.case = TRUE) ~ "AIPAC",
    TRUE ~ contributor_name # I ran this without the abbreviation and it made creating the plot very difficult.
  ))
allPAC
```

```{r, fig.width=10, fig.height=5, out.width="100%"}
ggplot(allPAC, aes(x = cand, y = total, fill = contributor_name)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "Candidate",
    y = "Total (in dollars)",
    title = "Distribution of PAC Contributions",
    fill = "PAC"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(fill = guide_legend(nrow = 3)) +
  scale_fill_discrete(labels = function(x) str_wrap(x, width = 25))
```

Trone and Delaney both take a fair amount of money from PACs. As we can see, Delaney has a more even distribution than Trone, but that is mostly because she takes considerably more money from PACs in general. We saw earlier that Trone take around \$117,000 in PAC money while Delaney takes over \$720,000 in PAC money.

Let's look at these PACs and see what interests they represent

For Trone:

-   [AIPAC](https://www.aipac.org) is an organization seemingly composed to influence law makers to promote the relationship between the United States and Israel. 

-   [SWING LEFT](https://swingleft.org) is an organization that identifies swing districts and tries to turn them blue.

-   [BROOKDALE SENIOR LIVING PAC](https://www.google.com/url?sa=t&source=web&rct=j&opi=89978449&url=https://www.brookdale.com/en.html&ved=2ahUKEwijy6_VuOiTAxWWjIkEHeL-DIwQFnoECB8QAQ&usg=AOvVaw2JQRB2K7-XFynqtgfQIdOk) seems to be an elder care provider that also advocates for seniors politically.

For Delaney:

-   [AIPAC](https://www.aipac.org) here again... directly from their website "AIPAC brings together Democrats and Republicans to advance our shared mission. Building bipartisan support for the U.S.-Israel relationship is an American value we are proud to champion."

-   [DEMOCRACY SUMMER 2026](https://jamieraskin.com/democracy-summer/) is an organization that introduces new democratic leaders to politics.

-   [AMERIPAC: THE FUND FOR A GREATER AMERICA](https://www.ameripacfund.com/ameripac-fund-greater-america) is an organization that helps democrats get elected to congress.

These organizations and their contributions show us a major part of each candidate’s financial support. Delaney receives funding from several PACs that focus on elevating new voices within the Democratic Party. Trone, meanwhile, is supported by groups that advocate for issues affecting older Americans.

However, for both candidates, the largest share of PAC funding comes from AIPAC. This stands out given the organization’s stated mission: “Building bipartisan support for the U.S.-Israel relationship is an American value we are proud to champion.”

Taken together, this suggests that while each candidate draws support from issue-specific groups, both are ultimately reliant on the same dominant national political donor network.


## Conclusion
Whether funding comes from individuals, organizations, or PACs, understanding who representatives are responsive to requires close attention to their financial support

For both Trone and Delaney, we see a similar pattern. Some of the wealthiest individuals in all of congress receive the majority of their individual donations from large donations, and they both get a considerable amount of money from the same PAC.

This similarity puts voters in a difficult position. Neither candidate appears to be primarily funded by the people they claim to represent. As a result, it becomes harder to evaluate their policy positions and to vote with confidence that a candidate’s priorities align with your own interests.

## Work in Progress

Below is a part of this project that I want to add, but I need to flesh it out more. The goal here is to display where the donors are and to see if out-of-state donors influence policy.

```{r}
## Average distance by Contributor
# Clean all data ZIP codes and select only necessary variables
MD_map_data <- df_filtered(all_data) %>% 
  mutate(
    contributor_zip = str_sub(contributor_zip, 1, 5),
    contributor_zip = str_pad(contributor_zip, 5, pad = "0")) %>% 
  select(
    committee_id, committee_name, report_year, entity_type, entity_type_desc,
    contributor_name, contributor_city, contributor_state, contributor_zip,
    contributor_id, is_individual, contribution_receipt_amount) %>% 
  group_by(committee_name, contributor_name) %>% 
  mutate(total = sum(contribution_receipt_amount, na.rm = TRUE)) %>% 
  ungroup()

lat_long_tbl <- MD_map_data %>% 
  left_join(
    ZipGeography %>% select(ZIP, Latitude, Longitude),
    by = c("contributor_zip" = "ZIP")
  ) %>% 
  filter(!is.na(Latitude)) # Remove around 100 lines where lat/long data isn't available.
```
This cleans up the zip code column and also joins a lat/long table so I can plot the donors on a map.
```{r}
# State Contribution Map [WIP] ----------------------------------------------
## https://forum.posit.co/t/how-to-make-markers-have-different-colors-based-on-specific-variable-in-data-frame-using-leaflet-map/186922/3
max_contributor <- lat_long_tbl %>% 
  group_by(committee_name, contributor_name) %>% 
  summarise(
    sum_val = sum(contribution_receipt_amount),
    Latitude = mean(Latitude, na.rm = TRUE),
    Longitude = mean(Longitude, na.rm = TRUE),
    contributor_state = first(na.omit(contributor_state)),
    contributor_city = first(na.omit(contributor_city)),
    .groups = "drop"
  ) %>% 
  group_by(committee_name) %>% 
  slice_max(sum_val, n = 5) %>% 
  ungroup()

pal <- colorFactor(
  palette = c("#7B1FA2", "#F28E2B"),
  domain = c(
    "DAVID TRONE FOR CONGRESS",
    "APRIL MCCLAIN DELANEY FOR CONGRESS"
  )
)

DonationMap <-
  leaflet(lat_long_tbl) %>%
  addTiles() %>%
  addCircleMarkers(
    lng = ~Longitude,
    lat = ~Latitude,
    radius = 0.5,
    color = ~pal(committee_name),
    popup = ~paste0(
      "<b>CONTRIBUTION</b><br>",
      "Contributor: ", contributor_name, "<br>",
      "Contributor State: ", contributor_city, ", ", contributor_state, "<br>",
      "Recipient : ", committee_name, "<br>",
      "Total: $", comma(total)
      )
  ) %>%
  addMarkers(
    data = max_contributor,
    lng = ~Longitude,
    lat = ~Latitude,
    popup = ~paste0(
      "<b>TOP CONTRIBUTOR</b><br>",
      "Contributor: ", contributor_name, "<br>",
      "Contributor State: ", contributor_city, ", ", contributor_state, "<br>",
      "Recipient : ", committee_name, "<br>",
      "Total: $", comma(sum_val)
    )
  ) %>%
  setView(-98.55, 39.80, zoom = 4) %>% 
  
  addLegend(
    "topleft",
    pal = pal,
    values = ~committee_name,
    title = "Candidate",
    opacity = 1
  )
```
This works in the RMD, but I can't get it to render properly and keep the nd.html file like I need to. 
